%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

%\newcommand\date[1]{\textit{#1}}
%\def\dates#1{\datesaux#1\stop}
%\def\datesaux#1-#2\stop{
%  \date{#1}\thinspace--\thinspace\date{#2}}

\name{Andrew Negri} % Your name
\address{7017 S. Priest Dr. \#3111 \\ Tempe, AZ 85283} % Your address
\address{(949)~$\cdot$~878~$\cdot$~2232 \\ andrewnegri1@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Arizona State University} \hfill {\em Expected May 2018} \\
B.S. in Software Engineering, Minor in Business \smallskip \\
Overall GPA: 3.66 \textit{Dean's List}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Employment}

\begin{rSubsection}{GoDaddy}{May 2017 -- August 2017}{Software Development Intern}{Gilbert, AZ}
\item Created a plugin in Python that captured the web access data of over 600,000 customer sites for Hadoop processing in real time. Developed using CI/CD with Jenkins and deployed using Puppet.
\item Discovered over 1,000,000 customer data files that had not been deleted in the account deletion workflow and wrote a Bash script to manually remove them.
\item Built and deployed 5 proxy servers by following an extensive build process with Puppet and other command line tools.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Fitness Training Web Application}{February 2018 -- Present}{}{}
\item Devised a full stack web application for users to follow a selected workout program over time by setting goals, tracking individual workouts, and reviewing progress.
\item Created a REST API in Python using the Django framework.
\item Developed a web client in JavaScript using the Flux design pattern with React and Redux.
\item Authenticated users with JSON Web Tokens.
\end{rSubsection}

\begin{rSubsection}{Carbon Footprint Web Application}{October 2017 -- Present}{}{}
\item Co-developed a full stack web application that empowers individuals to uphold the Paris Agreement by taking a pledge and setting goals to reducer their carbon footprint.
\item Utilized MongoDB, Express, React, and Node.js for the technology stack.
\item Coordinated efforts between five colleagues and two external sponsors using Scrum.
\end{rSubsection}

\begin{rSubsection}{Drill Keeper Android App}{February 2016 -- Present}{}{}
\item Developed an application that serves as a digital drill book for use in marching bands.
\item Crafted an intuitive user interface that adheres to material design guidelines with XML using Android UI components.
\item Saved and passed data by serializing objects with JSON via the Gson library.
\item Released on the Google Play store and updated regularly. Used user feedback to find bugs and influence future development.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Java, Python, JavaScript, HTML, CSS, SQL \\
Frameworks & Node.js, Express, React, Redux, Django, Bootstrap  \\
Databases & MySQL, PostgreSQL, MongoDB \\
Tools/Other & Git, Puppet, Jenkins, Linux, Scrum, Jira

\end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------

\end{document}